---
title: "Practical Machine Learning"
author: "Shen Yang"
date: "March 22, 2015"
output: html_document
---

## Getting Data
```{r, echo=TRUE}
raw_training <- read.csv("pml-training.csv", header=TRUE, sep=",", na.strings=c("NA", "", "#DIV/0!"))
raw_testing <- read.csv("pml-testing.csv", header=TRUE, sep=",", na.strings=c("NA", "", "#DIV/0!"))
str(raw_training)
```

## Cleaning Data
As can be seen, there are a large number of empty records or NA's in the training data. To clean the data up, we will
remove columns that have more than 10% NA's. We will also remove columns that are of no interest to
the model building.
```{r echo=TRUE}
## The first 7 columns are really some side info
raw_training <- raw_training[,-c(1:7)]
## Find columns with >= 90% non-NA
valid_columns <- c((colSums(!is.na(raw_training[,-ncol(raw_training)])) >= 0.9*nrow(raw_training)))
raw_training <- raw_training[, valid_columns]
```

## Setting Up Data Partition
60% data for training and 40% for testing
```{r echo=TRUE}
library(caret)
inTrain = createDataPartition(raw_training$classe, p=0.60, list=FALSE)
training = raw_training[inTrain,]
testing = raw_training[-inTrain,]
```

## Modelling
We will use random forest model.
```{r echo=TRUE}
library(randomForest)
rfmodel <- randomForest(classe~.,data=training)
rfmodel
```

## Evaluating Model
Evaluate the model results through confusion Matrix
```{r echo=TRUE}
confusionMatrix(predict(rfmodel,newdata=testing[,-ncol(testing)]),testing$classe)
```
Overall model accuracy is about 99.22% which is not too bad.


## Prediction Assignment Submission
Gerneratings files to be uploaded.
```{r echo=TRUE}
error_sample <- predict(rfmodel, raw_testing, type="class")

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(error_sample)
```